Stability of variational quantum dynamics with Gaussian approximants

### 2013-07-23 paper.tex
writing

>>>>

%% Finite phase space

The operator $|Γ〉$ acts on functions defined over the whole complex plane.  For states with high particle number, the smallest preimages have support far from the origin.  We can not compute with such functions: any discretisation will sample values of $f$ on a finite subset of the plane.  Unfortunately, the conditioning of these restricted operators will be worse than that of $|Γ〉$.  We have excluded the small preimages of the states with large particle number, so they must be represented by functions with support close to the origin, but with large norms.  Hence the restricted operators will have small singular values corresponding to states with many particles.

Define a restricted operator
$$|Γ_χ〉f=π^{-½}\int |α〉e^{-½|α|²}χ(α*)f(α*)\,d²α.$$
For now, suppose that $χ$ has circular symmetry, with $χ(z)=χ(|z|)$.  The most obvious examples are characteristic functions, where $χ$ is 1 inside a circle of radius $b$, and 0 outside.  However, the formalism allows more gradual truncation as well.  We can rewrite this
$$\eqalign{|Γ_χ〉f&=π^{-½}∑_n(n!)^{-½}|n〉\int αⁿe^{-|α|²}χ(α*)f(α*)\,d²α\cr
	&=π^{-½}∑_n(n!)^{-½}|n〉\int_0^∞ r^{n+1}e^{-r²}χ(r)\int_0^{2π}f(re^{-iθ})e^{inθ}\,dθdr\cr
	&=2\sqrt π∑_n(n!)^{-½}|n〉\int_0^∞ r^{n+1}e^{-r²}χ(r)f_n(r)dr,}$$
where
$$f(re^{iθ})=∑_{m=-∞}^∞ f_m(r)e^{imθ}.$$
Presumably, the right singular vectors have the $f_n$ of least norm such that 
$$2\sqrt π(n!)^{-½}\int_0^∞ r^{n+1}e^{-r²}χ(r)f_n(r)dr=1.$$

What is the appropriate norm to use?  In the case that $χ$ is a characteristic function on the domain $D$, it is presumably the truncated Bargmann norm
$$〈g,f〉=\int_D e^{-|α|²}g*(α)f(α)\,d²α=\int e^{-|α|²}χ(α)g*(α)f(α)\,d²α.$$
Note that this is only an inner product when $g$ and $f$ are restricted to $D$.  In this case, we wish to minimise 
$$\|f_n\|²=2π\int_0^b re^{-r²}f²_n(r)\,dr,$$
given 
$$2\sqrt π(n!)^{-½}\int_0^b r^{n+1}e^{-r²}f_n(r)dr=1.$$
If one considers changing $f$ by $Δa$ in an interval around $a$, the Lagrange condition is
$$re^{-r²}f_n(r)\propto r^{n+1}e^{-r²},$$
or 
$$f_n(r)\propto rⁿ.$$
The analytic functions still win.  
In this case, the integrals are identical, so, for the preimage of $|n〉$,
$$\|f_n\|²=\sqrt{πn!},$$
and, presuming $|n〉$ is the singular vector, the singular value is
$$σ_n=(πn!)^{-1/4}.$$
I've done something wrong, because the result doesn't depend on $b$.
